---
title: "AVL_Codes_Old"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
library(tidyverse)
library(ggplot2)
library(caret)
library(httr)
library(jsonlite)
# library(RTwitterV2)
library(tweetscores)
library(rtweet)
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(out.width = "100%", fig.align = 'center')

load("All_Data/Final Data with Treatment Assignments.Rdata")
load("experiment.RData")
```


## Important Dates

# 10.13             Data starts. Initial suvery taken
# 10.17             Experiment Starts (following bots)
# 11.23-27          Post Survey taken
# 02.01             This Data ends



ID: 17639368


```{r}
length(unique(final_assignments$id_str))
length(unique((final_assignments %>% filter(treat == "1"))$id_str))
length(unique((final_assignments %>% filter(treat == "0"))$id_str))
```


```{r}
load("result_ip_match.RData")
result_ip_match %>% filter(ideal_point == -Inf)
result_ip_match = result_ip_match %>% mutate(ideal_point = ifelse(ideal_point == -Inf, -2, ideal_point))
current_ip_oldref = result_ip_match %>% filter(estimate == "old") %>% select(id_str, ideal_point) %>% mutate(Date = "2022-11-13")
current_ip_oldref = result_ip_match %>% filter(estimate == "old") %>% select(id_str, ideal_point) %>% mutate(Date = "2022-11-13")
```

```{r}
all_ip_oldref = rbind(experiment2, current_ip_oldref) %>% filter(id_str %in% current_ip_oldref$id_str)
all_ip_oldref = rbind(experiment2, current_ip_oldref) %>% filter(id_str %in% current_ip_oldref$id_str)
```

```{r}
all_ip_oldref_info <- left_join(all_ip_oldref, final_assignments, by=c("id_str" = "id_str")) %>% 
  mutate(ideal_point = as.numeric(ideal_point)) %>% select(id_str, ideal_point, Date, party_ID, treat, party_strength) %>% na.omit()

all_ip_oldref_info <- left_join(all_ip_oldref, final_assignments, by=c("id_str" = "id_str")) %>% 
  mutate(ideal_point = as.numeric(ideal_point)) %>% select(id_str, ideal_point, Date, party_ID, treat, party_strength) %>% na.omit()
```



```{r}
all_ip_oldref_info %>% filter(Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>% group_by(Date, party_ID)%>% summarise(mean(ideal_point),n())


all_ip_oldref_info %>% filter(Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>% group_by(Date)%>% summarise(mean(ideal_point),n())
```



```{r, fig.width=15, fig.height=4.5, warning=F}
library(gridExtra)
# Define the blue and red colors
blue_color <- "#0000FF"
red_color <- "#FF0000"

# Create the blue and red color palette
color_palette <- c(blue_color, red_color)


legend <- cowplot::get_legend(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_density(alpha = 0.3) +
    labs(title = "All Treatment", y = "Density", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    scale_color_manual(values = color_palette) + facet_wrap(~Date)
)

grid.arrange(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_density(alpha = 0.3) +
    labs(title = "Treated Group", y = "Density", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  all_ip_oldref_info %>% filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_density(alpha = 0.3) +
    labs(title = "Control Group", y = "Density", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  nrow = 1,
  right = legend
)



legend <- cowplot::get_legend(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_density(alpha = 0.3) +
    labs(title = "All Treatment", y = "Density", x = "Ideal Points", color = "Party Affiliation") +
    scale_color_manual(values = color_palette) + facet_wrap(~Date)
)

grid.arrange(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_density(alpha = 0.3) +
    labs(title = "All Treatment", y = "Density", x = "Ideal Points", color = "Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  all_ip_oldref_info %>% filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_density(alpha = 0.3) +
    labs(title = "All Control", y = "Density", x = "Ideal Points", color = "Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  nrow = 1,
  right = legend
)
```

```{r, fig.width=15, fig.height=4.5, warning=F}
library(gridExtra)
# Define the blue and red colors
blue_color <- "#0000FF"
red_color <- "#FF0000"

# Create the blue and red color palette
color_palette <- c(blue_color, red_color)

legend <- cowplot::get_legend(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "All Treatment", y = "Counts", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    scale_color_manual(values = color_palette) + facet_wrap(~Date)
)

grid.arrange(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    # filter(party_ID == "Democrat") %>% 
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "Treated", y = "Counts", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  all_ip_oldref_info %>% filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    # filter(party_ID == "Democrat") %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "Control", y = "Counts", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  nrow = 1,
  right = legend
)


grid.arrange(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    filter(party_ID == "Democrat") %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "All Treatment", y = "Counts", x = "Ideal Points", color = "Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  all_ip_oldref_info %>% filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    filter(party_ID == "Democrat") %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "All Control", y = "Counts", x = "Ideal Points", color = "Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  nrow = 1,
  right = legend
)


grid.arrange(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    filter(party_ID != "Democrat") %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "All Treatment", y = "Counts", x = "Ideal Points", color = "Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = "#FF0000") + 
    theme(legend.position = "none"),
  
  all_ip_oldref_info %>% filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    filter(party_ID != "Democrat") %>%
    ggplot(aes(x = ideal_point, color = party_ID)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "All Control", y = "Counts", x = "Ideal Points", color = "Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = "#FF0000") + 
    theme(legend.position = "none"),
  
  nrow = 1,
  right = legend
)
```

```{r, fig.width=15, fig.height=4.5, warning=F}
# Define the blue and red colors
blue_color <- "blue4"
red_color <- "red4"
blue2_color <- "dodgerblue1"
red2_color <- "hotpink1"

# Create the blue and red color palette
color_palette <- c(blue_color, red_color, blue2_color, red2_color)


legend <- cowplot::get_legend(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_strength)) +
    geom_density(alpha = 0.3) +
    labs(title = "All Treatment", y = "Density", x = "Ideal Points", color = "Party Affiliation") +
    scale_color_manual(values = color_palette) + facet_wrap(~Date)
)

grid.arrange(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_strength)) +
    geom_density(alpha = 0.3) +
    labs(title = "Treated", y = "Density", x = "Ideal Points", color = "Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  all_ip_oldref_info %>% filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_strength)) +
    geom_density(alpha = 0.3) +
    labs(title = "Control", y = "Density", x = "Ideal Points", color = "Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  nrow = 1,
  right = legend
)




# Create the blue and red color palette
color_palette <- c(blue_color, blue2_color, red2_color, red_color)


legend <- cowplot::get_legend(
  all_ip_oldref_info %>% 
    filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    mutate(party_strength = factor(party_strength, levels = c("Strong Democrat", "Weak Democrat", "Weak Republican", "Strong Republican"))) %>% 
    ggplot(aes(ideal_point, color = party_strength)) +
    geom_boxplot() + coord_flip() + 
    labs(title = "Treated Group", y = "Party Affiliation", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = color_palette) + guides(colour = guide_legend(nrow = 1))
)

grid.arrange(
  all_ip_oldref_info %>% 
    filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    mutate(party_strength = factor(party_strength, levels = c("Strong Democrat", "Weak Democrat", "Weak Republican", "Strong Republican"))) %>% 
    ggplot(aes(ideal_point, color = party_strength)) +
    geom_boxplot() + coord_flip() + 
    labs(title = "Treated Group", y = "Party Affiliation", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = color_palette) + 
    theme(legend.position = "none", axis.text.x=element_blank(), axis.ticks.x=element_blank()),
  
  all_ip_oldref_info %>% 
    filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    mutate(party_strength = factor(party_strength, levels = c("Strong Democrat", "Weak Democrat", "Weak Republican", "Strong Republican"))) %>% 
    ggplot(aes(ideal_point, color = party_strength)) +
    geom_boxplot() + coord_flip() + 
    labs(title = "Control Group", y = "Party Affiliation", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = color_palette) + 
    theme(legend.position = "none", axis.text.x=element_blank(), axis.ticks.x=element_blank()),
  
  nrow = 1,
  bottom = legend
)

table(all_ip_oldref_info$party_strength)


# Create the blue and red color palette
color_palette <- c(blue_color, blue2_color, red2_color, red_color)
all_ip_oldref_info %>% 
    filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    mutate(party_strength = factor(party_strength, levels = c("Strong Democrat", "Weak Democrat", "Weak Republican", "Strong Republican"))) %>% 
    ggplot(aes(ideal_point, color = party_strength)) +
    geom_boxplot() + coord_flip() + 
    labs(title = "", y = "Party Affiliation", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = color_palette) + 
    theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) 



legend <- cowplot::get_legend(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    ggplot(aes(x = ideal_point, color = party_strength)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "All Treatment", y = "Counts", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    scale_color_manual(values = color_palette) + facet_wrap(~Date)
)

grid.arrange(
  all_ip_oldref_info %>% filter(treat == "1", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    # filter(party_ID == "Democrat") %>% 
    ggplot(aes(x = ideal_point, color = party_strength)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "Treated", y = "Counts", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) + scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  all_ip_oldref_info %>% filter(treat == "0", Date %in% c("2017-10-20", "2017-11-27", "2018-02-01", "2022-11-13")) %>%
    # filter(party_ID == "Democrat") %>%
    ggplot(aes(x = ideal_point, color = party_strength)) +
    geom_histogram(alpha = 0.3) +
    labs(title = "Control", y = "Counts", x = "Ideal Points", color = "Self-reported Party Affiliation") +
    facet_wrap(~Date) +  scale_color_manual(values = color_palette) + 
    theme(legend.position = "none"),
  
  nrow = 1,
  right = legend
)

```







# available size of data over time

```{r, fig.width=12}
experiment2 %>% group_by(Date) %>% summarise(available_data = n()) %>% ggplot(aes(x=Date,y=available_data)) + geom_point() + geom_line(aes(group = 1)) + theme(axis.text.x = element_text(angle = 60, vjust = 1, hjust=1))
```


# DID calculation
 
$$\hat \tau_{DID} = (\bar Y_{1, t+1}-\bar Y_{1, t}) - (\bar Y_{0, t+1}-\bar Y_{0, t}) $$
$$\hat \tau_{DID} = (\bar Y_{1, t+1}-\bar Y_{0, t+1}) - (\bar Y_{1, t}-\bar Y_{0, t}) $$


```{r}
# DEM
 
trt_ip_oldref_wider_dem = all_ip_oldref_info %>% filter(Date %in% c("2017-10-20","2022-11-13")) %>% filter(treat == 1, party_ID == "Democrat") %>% 
  pivot_wider(names_from = Date, values_from = ideal_point) %>% na.omit()

control_ip_oldref_wider_dem = all_ip_oldref_info %>% filter(Date %in% c("2017-10-20","2022-11-13")) %>% filter(treat == 0, party_ID == "Democrat") %>% 
  pivot_wider(names_from = Date, values_from = ideal_point) %>% na.omit()

# DID
DID_dem = (mean(trt_ip_oldref_wider_dem$`2022-11-13`) - mean(control_ip_oldref_wider_dem$`2022-11-13`) ) - (mean(trt_ip_oldref_wider_dem$`2017-10-20`) - mean(control_ip_oldref_wider_dem$`2017-10-20`))
DID_dem

control_change_dem = mean(control_ip_oldref_wider_dem$`2017-10-20`) - mean(control_ip_oldref_wider_dem$`2022-11-13`)
treat_start_dem = mean(trt_ip_oldref_wider_dem$`2017-10-20`)
treat_end_dem = mean(trt_ip_oldref_wider_dem$`2017-10-20`) - control_change_dem
```


```{r}
# REP 
trt_ip_oldref_wider_rep = all_ip_oldref_info %>% filter(Date %in% c("2017-10-20","2022-11-13")) %>% filter(treat == 1, party_ID == "Republican") %>% 
  pivot_wider(names_from = Date, values_from = ideal_point) %>% na.omit()

control_ip_oldref_wider_rep = all_ip_oldref_info %>% filter(Date %in% c("2017-10-20","2022-11-13")) %>% filter(treat == 0, party_ID == "Republican") %>% 
  pivot_wider(names_from = Date, values_from = ideal_point) %>% na.omit()

# DID
DID_rep = (mean(trt_ip_oldref_wider_rep$`2022-11-13`) - mean(control_ip_oldref_wider_rep$`2022-11-13`)) - 
(mean(trt_ip_oldref_wider_rep$`2017-10-20`) - mean(control_ip_oldref_wider_rep$`2017-10-20`))
DID_rep

control_change_rep = mean(control_ip_oldref_wider_rep$`2017-10-20`) - mean(control_ip_oldref_wider_rep$`2022-11-13`)
treat_start_rep = mean(trt_ip_oldref_wider_rep$`2017-10-20`) 
treat_end_rep = mean(trt_ip_oldref_wider_rep$`2017-10-20`) - control_change_rep
```

```{r}
mean(trt_ip_oldref_wider_rep$`2017-10-20`)
mean(control_ip_oldref_wider_rep$`2017-10-20`)

mean(trt_ip_oldref_wider_rep$`2022-11-13`)
mean(control_ip_oldref_wider_rep$`2022-11-13`)



median(trt_ip_oldref_wider_rep$`2017-10-20`)
median(control_ip_oldref_wider_rep$`2017-10-20`)

median(trt_ip_oldref_wider_rep$`2022-11-13`)
median(control_ip_oldref_wider_rep$`2022-11-13`)
```

# DID plots 

```{r}
# Define the blue and red colors
blue_color <- "#0000FF"
red_color <- "#FF0000"
color_palette <- c(blue_color, red_color)


# all_ip_oldref_info %>% filter(treat == "1", party_ID != "Democrat", Date %in% c("2017-10-20", "2022-11-13")) %>%
#   ggplot(aes(y=ideal_point, color = Date, x = Date)) + geom_boxplot() + labs(title = "Republican Treatment")

rbind(trt_ip_oldref_wider_dem,trt_ip_oldref_wider_rep)[,-1] %>% pivot_longer(cols = 4:5, names_to = "Date", values_to = "ideal_point") %>%
  ggplot(aes(y=ideal_point, color = party_ID, x = Date)) + geom_boxplot() + labs(title = "Treatment") + 
  stat_summary(fun.y=mean, geom="point", shape=20, size=5) + 
  scale_color_manual(values = color_palette)

rbind(control_ip_oldref_wider_dem,control_ip_oldref_wider_rep)[,-1]  %>% pivot_longer(cols = 4:5, names_to = "Date", values_to = "ideal_point") %>%
  ggplot(aes(y=ideal_point, color = party_ID, x = Date)) + geom_boxplot() + labs(title = "Control") + 
  stat_summary(fun.y=mean, geom="point", shape=20, size=5) + 
  scale_color_manual(values = color_palette)



rbind(trt_ip_oldref_wider_dem,control_ip_oldref_wider_dem)[,-1] %>% pivot_longer(cols = 4:5, names_to = "Date", values_to = "ideal_point") %>%
  ggplot(aes(y = ideal_point, x = Date, color = factor(treat))) +
  stat_summary(fun.y = mean, geom = "point", shape = 20, size = 5) +
  stat_summary(fun.y = mean, geom = "line", aes(group = factor(treat)), size = 1) +
  labs(title = "Democrat") + 
  scale_color_manual(values = color_palette)
  
rbind(trt_ip_oldref_wider_rep,control_ip_oldref_wider_rep)[,-1] %>% pivot_longer(cols = 4:5, names_to = "Date", values_to = "ideal_point") %>% 
  ggplot(aes(y = ideal_point, x = Date, color = factor(treat))) +
  stat_summary(fun.y = mean, geom = "point", shape = 20, size = 5) +
  stat_summary(fun.y = mean, geom = "line", aes(group = factor(treat)), size = 1) +
  labs(title = "Republican") + 
  scale_color_manual(values = color_palette)
```


```{r, fig.width=12, fig.height=3, warning=F}
color_palette <- c("orange", "yellowgreen")


legend <- cowplot::get_legend(
rbind(trt_ip_oldref_wider_dem,control_ip_oldref_wider_dem)[,-1] %>% pivot_longer(cols = 4:5, names_to = "Date", values_to = "ideal_point") %>% 
  ggplot(aes(y = ideal_point, x = Date, color = factor(treat))) +
  stat_summary(fun.y = mean, geom = "point", shape = 20, size = 5) +
  stat_summary(fun.y = mean, geom = "line", aes(group = factor(treat)), size = 1) +
  labs(title = "Democrat", color = "Treatment", y = "Average Ideal Point") + 
  scale_color_manual(values = color_palette) 
)

grid.arrange(
rbind(trt_ip_oldref_wider_dem,control_ip_oldref_wider_dem)[,-1] %>% pivot_longer(cols = 4:5, names_to = "Date", values_to = "ideal_point") %>% 
  ggplot(aes(y = ideal_point, x = Date, color = factor(treat))) +
  stat_summary(fun.y = mean, geom = "point", shape = 20, size = 5) +
  stat_summary(fun.y = mean, geom = "line", aes(group = factor(treat)), size = 1) +
  geom_point(data = data.frame(Date = c("2017-10-20","2022-11-13"), ideal_point = c(treat_start_dem, treat_end_dem)), 
            aes(x = Date, y = ideal_point), color ="yellowgreen", shape = 1, size = 3) + 
  geom_line(data = data.frame(Date = c("2017-10-20","2022-11-13"), ideal_point = c(treat_start_dem, treat_end_dem)), 
            aes(x = Date, y = ideal_point, group = 1), color ="yellowgreen", linetype = "dashed") +
  labs(title = "Democrat", color = "Treatment", y = "Average Ideal Point") + 
  scale_color_manual(values = color_palette) + theme(legend.position = "none")
,  
rbind(trt_ip_oldref_wider_rep,control_ip_oldref_wider_rep)[,-1] %>% pivot_longer(cols = 4:5, names_to = "Date", values_to = "ideal_point") %>% 
  ggplot(aes(y = ideal_point, x = Date)) +
  stat_summary(fun.y = mean, geom = "point", aes(color = factor(treat)), shape = 20, size = 5) +
  stat_summary(fun.y = mean, geom = "line", aes(color = factor(treat), group = factor(treat)), size = 1) +
  geom_point(data = data.frame(Date = c("2017-10-20","2022-11-13"), ideal_point = c(treat_start_rep, treat_end_rep)), 
            aes(x = Date, y = ideal_point), color ="yellowgreen", shape = 1, size = 3) + 
  geom_line(data = data.frame(Date = c("2017-10-20","2022-11-13"), ideal_point = c(treat_start_rep, treat_end_rep)), 
            aes(x = Date, y = ideal_point, group = 1), color ="yellowgreen", linetype = "dashed") +
  labs(title = "Republican", color = "Treatment", y = "Average Ideal Point") + 
  scale_color_manual(values = color_palette) + theme(legend.position = "none"), 
  nrow = 1,   
  right = legend
)
```





```{r}
# var
var_dem = var(trt_ip_oldref_wider_dem$`2017-10-20`) / length(trt_ip_oldref_wider_dem$`2017-10-20`) + 
var(trt_ip_oldref_wider_dem$`2022-11-13`) / length(trt_ip_oldref_wider_dem$`2022-11-13`) + 
var(control_ip_oldref_wider_dem$`2017-10-20`) / length(control_ip_oldref_wider_dem$`2017-10-20`) + 
var(control_ip_oldref_wider_dem$`2022-11-13`) / length(control_ip_oldref_wider_dem$`2022-11-13`) 
var_dem

var_rep = var(trt_ip_oldref_wider_rep$`2017-10-20`) / length(trt_ip_oldref_wider_rep$`2017-10-20`) + 
var(trt_ip_oldref_wider_rep$`2022-11-13`) / length(trt_ip_oldref_wider_rep$`2022-11-13`) + 
var(control_ip_oldref_wider_rep$`2017-10-20`) / length(control_ip_oldref_wider_rep$`2017-10-20`) + 
var(control_ip_oldref_wider_rep$`2022-11-13`) / length(control_ip_oldref_wider_rep$`2022-11-13`) 
var_rep
```


```{r}
# interval
# Dem
c(DID_dem, sqrt(var_dem))
DID_dem + c(-1,1) * 1.96 * sqrt(var_dem)
```

```{r}
# Rep
c(DID_rep,  sqrt(var_rep))
DID_rep + c(-1,1) * 1.96 * sqrt(var_rep)
```



# DID Regression formulation

<!-- \alpha_i &\equiv \alpha+ \gamma A_i\\ -->

$$
\begin{aligned}
Y_{it} &= \alpha_i+\lambda_t+\rho \mathrm{D}_{i t}+ \delta \mathrm{X}_{i t}+ \epsilon_{it} 
\end{aligned}
$$

### Democratic regression

```{r}
dem_avail = rbind(trt_ip_oldref_wider_dem, control_ip_oldref_wider_dem) %>% 
  left_join(final_assignments, by = "id_str") %>% 
  pivot_longer(cols = 5:6, names_to = "Time", values_to = "ideal_point") %>% 
  select(id_str, party_ID.x, treat.x, Time, ideal_point, gender_of, age, race_of, party_strength.x, freq_twitter, political, percent_co_party) %>% 
  mutate(Time_to_treat = ifelse(Time == "2017-10-20", 0, 1)) %>% 
  mutate(D_it = treat.x * Time_to_treat) 


dem_lm_1 = lm(ideal_point ~ id_str + Time + D_it - 1, data = dem_avail)
dem_lm_1_summ = summary(dem_lm_1)
tail(dem_lm_1_summ$coefficients, 2)
tail(confint(dem_lm_1, level = 0.9),1)

# more covariates
dem_lm_2 = lm(ideal_point ~ id_str + Time + age + race_of + gender_of + freq_twitter + political + D_it - 1, data = dem_avail)
dem_lm_2_summ = summary(dem_lm_2)
tail(dem_lm_2_summ$coefficients, 2)
tail(confint(dem_lm_2),1)


# random-effects model (with random intercept)
dem_re = lme4::lmer(ideal_point ~ Time + D_it + (1 | id_str) - 1, data = dem_avail)
summ_lmer = summary(dem_re)
tail(summ_lmer$coefficients, 1)[1]
tail(confint(dem_re, method="Wald"),1)
```


```{r}
# more days
all_dem_all_day = all_ip_oldref_info %>% 
    filter(Date %in% c("2017-10-13", "2017-10-20", "2017-11-23", "2017-11-27", "2018-02-01", "2022-11-13"))%>%
    left_join(final_assignments, by = "id_str") %>% 
  select(id_str, Date, party_ID.x, treat.x, ideal_point, gender_of, age, race_of, party_strength.x, freq_twitter, political, percent_co_party) %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Time = ifelse(Date == "2017-10-13", 0, Date - as.Date("2017-10-13"))) %>% 
  mutate(Time_to_treat = ifelse(Time <= 42, 0, 1)) %>% 
  mutate(D_it = treat.x * Time_to_treat) 


dem_lm_all = lm(ideal_point ~ id_str + factor(Date) + D_it - 1, data = all_dem_all_day)
dem_lm_all_summ = summary(dem_lm_all)
tail(dem_lm_all_summ$coefficients, 5)
tail(confint(dem_lm_all, level = 0.9) ,5)


# dem_lm_all = lm(ideal_point ~ id_str + factor(Date) + age + race_of + gender_of + freq_twitter + political + D_it - 1, 
#                 data = all_dem_all_day)
# dem_lm_all_summ = summary(dem_lm_all)
# tail(dem_lm_all_summ$coefficients, 5)
# tail(confint(dem_lm_all),5)
```


### Republican regression

```{r}
rep_avail = rbind(trt_ip_oldref_wider_rep,control_ip_oldref_wider_rep) %>% left_join(final_assignments, by = "id_str") %>% 
  pivot_longer(cols = 5:6, names_to = "Time", values_to = "ideal_point") %>% 
  select(id_str, party_ID.x, treat.x, Time, ideal_point, gender_of, age, race_of, party_strength.x, freq_twitter, political, percent_co_party) %>% 
  mutate(Time_to_treat = ifelse(Time == "2017-10-20", 0, 1)) %>% 
  mutate(D_it = treat.x * Time_to_treat) 

rep_lm_1 = lm(ideal_point ~ id_str + Time + D_it - 1, data = rep_avail)
rep_lm_1_summ = summary(rep_lm_1)
tail(rep_lm_1_summ$coefficients, 2)
tail(confint(rep_lm_1, level = 0.9),1)

# covariates
rep_lm_2 = lm(ideal_point ~ id_str + Time + age + race_of + gender_of + freq_twitter + political + D_it - 1, data = rep_avail)
rep_lm_2_summ = summary(rep_lm_2)
tail(rep_lm_2_summ$coefficients, 2)
tail(confint(rep_lm_2),1)

# random-effects model (with random intercept)
rep_re = lme4::lmer(ideal_point ~ Time + D_it + (1 | id_str) - 1, data = rep_avail)
summ_lmer = summary(rep_re)
tail(summ_lmer$coefficients, 1)[1]
tail(confint(rep_re, method="Wald"),1)
```


```{r}
# more days
all_rep_all_day = all_ip_oldref_info %>% filter(party_ID != "Democrat") %>% 
    filter(Date %in% c("2017-10-13", "2017-10-20", "2017-11-23", "2017-11-27", "2018-02-01", "2022-11-13"))%>%
    left_join(final_assignments, by = "id_str") %>% 
  select(id_str, Date, party_ID.x, treat.x, ideal_point, gender_of, age, race_of, party_strength.x, freq_twitter, political, percent_co_party) %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Time = ifelse(Date == "2017-10-13", 0, Date - as.Date("2017-10-13"))) %>% 
  mutate(Time_to_treat = ifelse(Time <= 120, 0, 1)) %>% 
  mutate(D_it = treat.x * Time_to_treat) 


rep_lm_all = lm(ideal_point ~ id_str + factor(Time) + D_it - 1, data = all_rep_all_day)
rep_lm_all_summ = summary(rep_lm_all)
tail(rep_lm_all_summ$coefficients, 1)
tail(confint(rep_lm_all), 1)


rep_lm_all = lm(ideal_point ~ id_str + factor(Time) + age + race_of + gender_of + freq_twitter + political + D_it - 1, data = all_rep_all_day)
rep_lm_all_summ = summary(rep_lm_all)
tail(rep_lm_all_summ$coefficients, 2)
tail(confint(rep_lm_all),1)
```


```{r}
library(did)

all_dem_did = all_ip_oldref_info %>% filter(party_ID == "Democrat") %>% 
    filter(Date %in% c( "2017-10-20", "2017-11-23", "2022-11-13"))%>%
    left_join(final_assignments, by = "id_str") %>% 
  select(id_str, Date, party_ID.x, treat.x, ideal_point, gender_of, age, race_of, party_strength.x, freq_twitter, political, percent_co_party) %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Time = ifelse(Date == "2017-10-13", 0, Date - as.Date("2017-10-13"))) %>% 
  mutate(Time_to_treat = ifelse(Time <= 30, 0, 1)) %>% 
  mutate(D_it = treat.x * Time_to_treat) %>% 
  mutate(first_treat = ifelse(treat.x == 0, 0, 30)) %>% 
  mutate(id = as.numeric(id_str))

dem.attgt <- att_gt(yname = "ideal_point",
                   gname = "first_treat",
                   idname = "id",
                   tname = "Time",
                   xformla = ~1,
                   data = all_dem_did,
                   )

summary(dem.attgt)
ggdid(dem.attgt)




all_rep_did = all_ip_oldref_info %>% filter(party_ID != "Democrat") %>% 
    filter(Date %in% c("2017-10-20", "2017-11-23", "2022-11-13"))%>%
    left_join(final_assignments, by = "id_str") %>% 
  select(id_str, Date, party_ID.x, treat.x, ideal_point, gender_of, age, race_of, party_strength.x, freq_twitter, political, percent_co_party) %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Time = ifelse(Date == "2017-10-13", 0, Date - as.Date("2017-10-13"))) %>% 
  mutate(Time_to_treat = ifelse(Time <= 30, 0, 1)) %>% 
  mutate(D_it = treat.x * Time_to_treat) %>% 
  mutate(first_treat = ifelse(treat.x == 0, 0, 30)) %>% 
  mutate(id = as.numeric(id_str))

rep.attgt <- att_gt(yname = "ideal_point",
                   gname = "first_treat",
                   idname = "id",
                   tname = "Time",
                   xformla = ~1,
                   data = all_rep_did,
                   )

summary(rep.attgt)
ggdid(rep.attgt)
```



```{r}
all_dem_did = all_ip_oldref_info %>% filter(party_ID == "Democrat") %>% mutate(Date = as.Date(Date)) %>% 
    filter(Date >= c("2017-10-20"))%>%
    filter(Date <= "2017-11-28"| Date >= "2018-11-20") %>% 
    left_join(final_assignments, by = "id_str") %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Time = ifelse(Date == "2017-10-20", 0, Date - as.Date("2017-10-20"))) %>% 
  mutate(Time_to_treat = ifelse(Time <= 30, 0, 1)) %>% 
  mutate(D_it = treat.x * Time_to_treat) %>% 
  mutate(first_treat = ifelse(treat.x == 0, 0, 30)) %>% 
  mutate(id = as.numeric(id_str))

dem.attgt <- att_gt(yname = "ideal_point",
                   gname = "first_treat",
                   idname = "id",
                   tname = "Time",
                   xformla = ~1,
                   data = all_dem_did,
                   )

summary(dem.attgt)
ggdid(dem.attgt)




all_rep_did = all_ip_oldref_info %>% filter(party_ID != "Democrat") %>% mutate(Date = as.Date(Date)) %>% 
    filter(Date >= c("2017-10-20"))%>%
    filter(Date <= "2017-11-28"| Date >= "2018-11-20") %>% 
    left_join(final_assignments, by = "id_str") %>% 
    left_join(final_assignments, by = "id_str") %>% 
  mutate(Date = as.Date(Date)) %>% 
  mutate(Time = ifelse(Date == "2017-10-20", 0, Date - as.Date("2017-10-20"))) %>% 
  mutate(Time_to_treat = ifelse(Time <= 30, 0, 1)) %>% 
  mutate(D_it = treat.x * Time_to_treat) %>% 
  mutate(first_treat = ifelse(treat.x == 0, 0, 30)) %>% 
  mutate(id = as.numeric(id_str))

rep.attgt <- att_gt(yname = "ideal_point",
                   gname = "first_treat",
                   idname = "id",
                   tname = "Time",
                   xformla = ~1,
                   data = all_rep_did,
                   )

summary(rep.attgt)
ggdid(rep.attgt)
```


# Missing data analysis

1516 participants roughly at the start of experiment

340 do not have a match in `final_assignments` (1239 participants)

135 participants cannot be performed estimations back then 

337 were available then, but not available now 

704 analyzed participants 
Democrat: 439  Republican: 265 
0: 282         1: 422

```{r, fig.width=15, fig.height=4}
experiment2 %>% filter(Date == "2017-10-20") # 1516

experiment2 %>% filter(Date == "2017-10-20") %>% filter(!id_str %in% final_assignments$id_str) # 340

analyzed_ppl = experiment2 %>% filter(Date == "2017-10-20") %>% filter(id_str %in% final_assignments$id_str) %>% na.omit(ideal_point) %>% filter(id_str %in% current_ip_oldref$id_str)
missing_ppl = experiment2 %>% filter(Date == "2017-10-20") %>% filter(id_str %in% final_assignments$id_str) %>% na.omit(ideal_point) %>% filter(!id_str %in% current_ip_oldref$id_str)
unest_ppl = experiment2 %>% filter(Date == "2017-10-20") %>% filter(id_str %in% final_assignments$id_str) %>% filter(is.na(ideal_point))

analyzed_ppl = left_join(analyzed_ppl, final_assignments, by=c("id_str" = "id_str"))
missing_ppl = left_join(missing_ppl, final_assignments, by=c("id_str" = "id_str"))
unest_ppl = left_join(unest_ppl, final_assignments, by=c("id_str" = "id_str"))

# hist(analyzed_ppl$friends_count, col = "red", breaks = 100) 
# hist(unest_ppl$friends_count, col = "blue", add = TRUE) 
# ggplot() + geom_density(aes(analyzed_ppl$friends_count)) + geom_density(aes(unest_ppl$friends_count), color = "red")

summary(unest_ppl$friends_count)
summary(missing_ppl$friends_count)
summary(analyzed_ppl$friends_count)

par(mfrow = c(1, 3))
barplot(prop.table( table(unest_ppl$party_strength) ) , main = "Unestimatable", ylab = "Percentage")
barplot(prop.table( table(missing_ppl$party_strength) ) , main = "Missing", ylab = "Percentage")
barplot(prop.table( table(analyzed_ppl$party_strength) ), main = "Analyzed", ylab = "Percentage")

par(mfrow = c(1, 3))
barplot(prop.table( table(unest_ppl$party_strength) ) , main = "Unestimatable", ylab = "Percentage", ylim = c(0,0.4))
barplot(prop.table( table(missing_ppl$party_strength) ) , main = "Missing", ylab = "Percentage", ylim = c(0,0.4))
barplot(prop.table( table(analyzed_ppl$party_strength) ), main = "Analyzed", ylab = "Percentage", ylim = c(0,0.4))


par(mfrow = c(1, 3))
barplot(prop.table( table(unest_ppl$active_twitter) ) , main = "Unestimatable", ylab = "Percentage", ylim = c(0,0.8))
barplot(prop.table( table(missing_ppl$active_twitter) ) , main = "Missing", ylab = "Percentage", ylim = c(0,0.8))
barplot(prop.table( table(analyzed_ppl$active_twitter) ), main = "Analyzed", ylab = "Percentage", ylim = c(0,0.8))

par(mfrow = c(1, 3))
barplot(prop.table( table(unest_ppl$freq_twitter) ) , main = "Unestimatable", ylab = "Percentage", ylim = c(0,0.8))
barplot(prop.table( table(missing_ppl$freq_twitter) ) , main = "Missing", ylab = "Percentage", ylim = c(0,0.8))
barplot(prop.table( table(analyzed_ppl$freq_twitter) ), main = "Analyzed", ylab = "Percentage", ylim = c(0,0.8))


par(mfrow = c(1, 3))
barplot(prop.table( table(unest_ppl$party_ID) ) , main = "Unestimatable", ylab = "Percentage", ylim = c(0,0.7))
barplot(prop.table( table(missing_ppl$party_ID) ) , main = "Missing", ylab = "Percentage", ylim = c(0,0.7))
barplot(prop.table( table(analyzed_ppl$party_ID) ), main = "Analyzed", ylab = "Percentage", ylim = c(0,0.7))


par(mfrow = c(1, 1))
plot(density(unest_ppl$age), main = "Age Distribution", col = 1, lwd = 5)
lines(density(missing_ppl$age), col = 3, lwd = 5)
lines(density(analyzed_ppl$age), col = 6, lwd = 5)
legend(x = "topleft",box.lwd = 2 , title="Type", 
       legend=c("Unestimatable", "Missing", "Analyzed"), 
       fill = c(1,3,6))


table(analyzed_ppl$party_ID)
table(analyzed_ppl$treat)
```


# daily

```{r}
set.seed(202309)

dem_treat_50 = sample(size = 50, unique((all_ip_oldref_info %>% filter(treat == 1, party_ID == "Democrat"))$id_str))
dem_control_50 = sample(size = 50, unique((all_ip_oldref_info %>% filter(treat == 0, party_ID == "Democrat"))$id_str))
rep_treat_50 = sample(size = 50, unique((all_ip_oldref_info %>% filter(treat == 1, party_ID != "Democrat"))$id_str))
rep_control_50 = sample(size = 50, unique((all_ip_oldref_info %>% filter(treat == 0, party_ID != "Democrat"))$id_str))


all_ip_oldref_info %>% 
  filter(id_str %in% dem_treat_50) %>%
  filter(Date != "2022-11-13") %>% dplyr::select(id_str, Date, ideal_point) %>% pivot_wider(names_from = Date, values_from = ideal_point)

all_ip_oldref_info %>% 
  filter(id_str %in% dem_treat_50) %>%
  filter(Date != "2022-11-13") %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = id_str, group = id_str)) + 
  geom_line() + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + 
  labs(title = "A sample from Dem in Treatment") + theme(legend.position = "none")


all_ip_oldref_info %>% 
  filter(id_str %in% dem_control_50) %>%
  filter(Date != "2022-11-13") %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = id_str, group = id_str)) + 
  geom_line() + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + 
  labs(title = "A sample from Dem in Control") + theme(legend.position = "none")



all_ip_oldref_info %>% 
  filter(id_str %in% rep_treat_50) %>%
  filter(Date != "2022-11-13") %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = id_str, group = id_str)) + 
  geom_line() + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + 
  labs(title = "A sample from Rep in Treatment") + theme(legend.position = "none")


all_ip_oldref_info %>% 
  filter(id_str %in% rep_control_50) %>%
  filter(Date != "2022-11-13") %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = id_str, group = id_str)) + 
  geom_line() + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + 
  labs(title = "A sample from Rep in Control") + theme(legend.position = "none")
```


```{r}
set.seed(8848)

dem_treat_50 = sample(size = 50, unique((all_ip_oldref_info %>% filter(treat == 1, party_ID == "Democrat"))$id_str))
dem_control_50 = sample(size = 50, unique((all_ip_oldref_info %>% filter(treat == 0, party_ID == "Democrat"))$id_str))
rep_treat_50 = sample(size = 50, unique((all_ip_oldref_info %>% filter(treat == 1, party_ID != "Democrat"))$id_str))
rep_control_50 = sample(size = 50, unique((all_ip_oldref_info %>% filter(treat == 0, party_ID != "Democrat"))$id_str))


all_ip_oldref_info %>% 
  filter(id_str %in% dem_treat_50) %>%
  filter(Date != "2022-11-13") %>% dplyr::select(id_str, Date, ideal_point) %>% pivot_wider(names_from = Date, values_from = ideal_point)

all_ip_oldref_info %>% 
  filter(id_str %in% dem_treat_50) %>%
  filter(Date != "2022-11-13") %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = id_str, group = id_str)) + 
  geom_line() + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + 
  labs(title = "A sample from Dem in Treatment") + theme(legend.position = "none")


all_ip_oldref_info %>% 
  filter(id_str %in% dem_control_50) %>%
  filter(Date != "2022-11-13") %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = id_str, group = id_str)) + 
  geom_line() + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + 
  labs(title = "A sample from Dem in Control") + theme(legend.position = "none")



all_ip_oldref_info %>% 
  filter(id_str %in% rep_treat_50) %>%
  filter(Date != "2022-11-13") %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = id_str, group = id_str)) + 
  geom_line() + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + 
  labs(title = "A sample from Rep in Treatment") + theme(legend.position = "none")


all_ip_oldref_info %>% 
  filter(id_str %in% rep_control_50) %>%
  filter(Date != "2022-11-13") %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = id_str, group = id_str)) + 
  geom_line() + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + 
  labs(title = "A sample from Rep in Control") + theme(legend.position = "none")
```


# old reference elite

```{r}
# Load the knitr package
library(knitr)

# Print the table nicely using kable
kable(data.frame("Twitter Account" = elite_name, `Estimation in 2015` = est_2015, `Estimation in 2022` = est_2022))
```



