---
title: "AVL_Codes"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
library(mosaic)
library(caret)
library(httr)
library(jsonlite)
library(RTwitterV2)
library(tweetscores)
library(rtweet)
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(out.width = "100%", fig.align = 'center')

load("All_Data/Final Data with Treatment Assignments.Rdata")
```


## Learn to use twitter API 

Get started with R and V2 of the Twitter API

```{r}
# Three Bear Tokens used for authentication
bearer_token <- c("AAAAAAAAAAAAAAAAAAAAADyWigEAAAAAIe7qu2QxR%2FGkeNxjm2SzTyoFGgA%3DC6G0cgMpCe1GnIr0HmmE6xDOi5kGouAn6KYeTTKMXOMMcqPCMs")

bearer_token <- c("AAAAAAAAAAAAAAAAAAAAAG6uiAEAAAAA8d6sH90zLVN3SHmskBVo1r%2BQ4Tc%3DEUtpPHdbW5XW6tm6EQjIfQqQOu0tIRAyHjtVLuIbNnV1FKD84j")

bearer_token <- c("AAAAAAAAAAAAAAAAAAAAABoZjQEAAAAA0gWmqoUzlFKziClP1YhJTrpYjE4%3Dg5iWkyBV5OFJjdEVeYfjbTMmAP39qyhJQqsm0c7tKQwxB1VQrQ")

headers <- c(`Authorization` = sprintf('Bearer %s', bearer_token))
```


```{r}
# example of extracting user info
params <- list(`user.fields` = 'description',
               `expansions` = 'pinned_tweet_id')

handle <- c('p_barbera')
url_handle <-
  sprintf('https://api.twitter.com/2/users/by?usernames=%s', handle)

response <-
  httr::GET(url = url_handle,
            httr::add_headers(.headers = headers),
            query = params)
obj <- httr::content(response, as = "text")
print(obj)
```


```{r, eval = F}
# transform into more readable jason data
json_data <- fromJSON(obj, flatten = TRUE) %>% as.data.frame

final <-
  sprintf(
    "Handle: %s\nBio: %s\nPinned Tweet: %s",
    json_data$data.username,
    json_data$data.description,
    json_data$includes.tweets.text
  )

cat(final)
```


## RTwitterV2 provides basic user info

```{r}
# Basic user info
library(RTwitterV2)

test <- get_timelines_v2(token = bearer_token, user_id = "14273050", n = 100)

test <- get_user_v2(token = bearer_token, user_ids = "959432550400831488, 1006933394, 105839015")

get_user_v2(token = bearer_token, user_ids = "1006933394")

get_user_v2(token = bearer_token, user_ids = "105839015")

get_user_v2(token = bearer_token, user_ids = "1464259289573376003")

# 14273050: following 2649 
```


# Learn to set and use rtweet pacakge

```{r, eval = F}
library(rtweet)

auth_setup_default()

# Check
auth_has_default()

# default
auth_as()

# sepcify as my app token
my_app <- rtweet_app()
auth_as(my_app)

auth_get()

auth_sitrep()
```


```{r}
rtweet::lookup_users("271184449")

lookup_users(as_screenname("123456"))
```

```{r}
f <- get_friends("14273050", n = Inf, retryonratelimit = T)
f[,2]
```





# Get follower data

My twitter id: 1464259289573376003

```{r}
tweet_id <- "1464259289573376003"

url_handle <- glue::glue("https://api.twitter.com/2/users/{status_id}/following?", status_id = tweet_id)

params <- list(`user.fields` = 'created_at',
               `expansions` = 'pinned_tweet_id')

response <- httr::GET(url = url_handle,
                     httr::add_headers(.headers = headers))

obj <- httr::content(response, as = "text")

x <- rjson::fromJSON(obj)

x$data %>% 
  purrr::map_chr("id")

x$meta$next_token
```


## API Pagenization issue 

```{r}
get_following <- function(tweet_id){
  
  page <- 1
  full <- list()
  next_page_token <- ""
  
  repeat {
    cat("Grab Page:", page, "\n")   # keep track of pages (not necessary but could be useful)

    params <- list(`user.fields` = 'created_at',
               `expansions` = 'pinned_tweet_id')
  
  if (next_page_token == "")
    {url_handle <- 
      glue::glue("https://api.twitter.com/2/users/{status_id}/following?max_results=1000", 
                 status_id = tweet_id)}
  else
  {url_handle <- glue::glue("https://api.twitter.com/2/users/{status_id}/following?max_results=1000&pagination_token={page_token}", status_id = tweet_id, page_token = next_page_token)}
  
    response <- httr::GET(url = url_handle,
                     httr::add_headers(.headers = headers))
    
    obj <- httr::content(response, as = "text")
    
    x <- rjson::fromJSON(obj)
    full <- c(full, x$data %>% purrr::map_chr("id"))
    
    if (is.null(x$meta$next_token))
    {
      cat("Final Page Counts Stops at:", page, "\n")
      break
    }
    next_page_token <-x$meta$next_token
    page = page + 1
}
  return(unlist(full))
}
```


```{r}
# test on user
user_friends_14273050 <- get_following("14273050")
length(user_friends_14273050)


user_friends <- get_following("105839015")
length(user_friends)
```


# Get follower data at specific time point? 

## Not Possible right now

```{r}
tweet_id <- "14273050"

url_handle <- glue::glue("https://api.twitter.com/2/users/{status_id}/following?max_results=1000", status_id = tweet_id)

params <- list(`user.fields` = 'created_at',
               `expansions` = 'pinned_tweet_id')

response <- httr::GET(url = url_handle,
                     httr::add_headers(.headers = headers))

obj <- httr::content(response, as = "text")

x <- rjson::fromJSON(obj)

x$data %>% 
  purrr::map_chr("id")
```



## Barbera


```{r, warning=F}
library(tweetscores)

  # Barbera's authentication does not work now
 # my_oauth <- list(consumer_key = "Ut4TOAU9P1xZBXV9NUoSL5aOV",
 #   consumer_secret = "7NjtXUgNbENHVxKlUAA96HisXS73xMHwDVyW9MUXVE2Ud7DzJi",
 #   access_token="dTVYRUtJSFZ1V19fM0dwS05mekg6MTpjaQ",
 #   access_token_secret = "rqKmQkBO8vRExhTbmU2vdprfAnwWKThKcjGEKmczt2Y2t7-bsq")

 # friends <- getFriends(screen_name="p_barbera", oauth=my_oauth)
 # results <- estimateIdeology(tweet_id,  friends)
 

# rtweet::lookup_users("142915704")


tweet_id <- "142915704"
user_friends <- rtweet::get_friends(tweet_id, n = Inf, retryonratelimit = T)[,2]
  
results <- tweetscores::estimateIdeology(user = tweet_id,  friends = user_friends$to_id, verbose = F)

summary(results)

tracePlot(results, "theta")
plot(results)

# mean(c(results$samples[,1,2],results$samples[,2,2]))

estimateIdeology2(user = tweet_id, friends = user_friends$to_id)

```




## Our network data from Oct 2017

```{r}
all_days <- c("2017-11-27")
user_ids.txt <- list.files(paste("All_Data/Friends/", all_days, sep=""), pattern = "[0-9].txt")
user_ids <- as.numeric(gsub("([0-9]+).*$", "\\1", user_ids.txt))
  
filenames <- list.files(paste("All_Data/Friends/", all_days, sep=""), pattern = "[0-9].txt", full.names = T)
network_ids <- lapply(filenames, scan)
```


```{r, message = F, eval = F}
all_days <- list.files("All_Data/Friends/", full.names = F)

# all_days <- c("2017-10-13", "2017-10-14", "2017-10-15") # test

day_user_friend <- list()
ip <- list()

for (i in seq_along(all_days))
{
  user_ids.txt <- list.files(paste("All_Data/Friends/", all_days[i], sep=""), pattern = "[0-9].txt")
  user_ids <- as.numeric(gsub("([0-9]+).*$", "\\1", user_ids.txt))
  
  filenames <- list.files(paste("All_Data/Friends/", all_days[i], sep=""), pattern = "[0-9].txt", full.names = T)
  network_ids <- lapply(filenames, scan)
  
  user_friends_list <- vector(mode = "list", length = length(user_ids))
  for (j in seq_along(user_ids))
  {
    user_friends_list[[j]] <- list(user_ids[j],
                                   network_ids[[j]])
  }
  
  
  ideal_point <- c()
  
  for (k in seq_along(user_friends_list)) {
    skip_to_next = FALSE
    
    tryCatch(
      ideal_point[k] <-
        estimateIdeology2(user_friends_list[[k]][[1]], user_friends_list[[k]][[2]]),
      error = function(e) {skip_to_next = TRUE}
    )
    
    if (skip_to_next) {next}
  }
  
  one_day_user_friend <- as_tibble(cbind(user_ids, ideal_point, rep(all_days[i], length(user_ids))))
  colnames(one_day_user_friend) <- c("user_ids", "ideal_point", "Date")
  ip[[i]] <- one_day_user_friend
}

```


```{r}
experiment <- bind_rows(ip) # experiment is the daily data in 2017-18
# save(experiment, file = "experiment.RData")
# load("experiment.RData") # user ids and their ideal points estimated during the experiment

```


```{r}
user_ids.txt1013 <- list.files(paste("All_Data/Friends/", "2017-10-13", sep=""), pattern = "[0-9].txt")
user_ids1013 <- as.numeric(gsub("([0-9]+).*$", "\\1", user_ids.txt1013))
length(user_ids1013)
```


## Important Dates

# 10.13             Data starts. Initial suvery taken
# 10.17             Experiment Starts (following bots)
# 11.23-27          Post Survey taken
# 02.01             This Data ends

```{r}
length(unique(final_assignments$id_str))
length(unique((final_assignments %>% filter(treat == "1"))$id_str))
length(unique((final_assignments %>% filter(treat == "0"))$id_str))
```


```{r, warning=F}
experiment_assign <- left_join(experiment, final_assignments, by=c("user_ids" = "id_str")) %>% 
  mutate(ideal_point = as.numeric(ideal_point))

set.seed(123456)

sample_30 <- sample(size = 30, unique((experiment_assign %>% filter(treat == "1"))$user_ids))

experiment_assign %>% filter(user_ids %in% sample_30) %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, color = user_ids, group = user_ids)) + geom_line() + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + labs(title = "A sample of 30 from Treatment")


experiment_assign %>% filter(treat == "1", Date %in% c( "2017-10-13", "2017-11-27", "2018-02-01") ) %>% 
  ggplot(aes(x=ideal_point, color = Date)) + geom_density(alpha=0.3) + labs(title = "Treatment")


experiment_assign %>% filter(treat == "1", Date %in% c("2017-10-13")) %>% 
  ggplot(aes(y=ideal_point, x = party_ID)) + geom_boxplot()+ labs(title = "Treatment")


experiment_assign %>% filter(treat == "1", party_ID == "Republican", Date %in% c("2017-10-16", "2017-11-27", "2018-02-01")) %>%
  ggplot(aes(x=ideal_point, color = Date, fill = Date)) + geom_density(alpha=0.3) + labs(title = "Republican Treatment")

experiment_assign %>% filter(treat == "1", party_ID == "Democrat", Date %in% c("2017-10-16","2017-11-27", "2018-02-01") ) %>% 
  ggplot(aes(x=ideal_point, color = Date, fill = Date)) + geom_density(alpha=0.3) + labs(title = "Democrat Treatment")
```


```{r}
experiment %>%  mutate(ideal_point = as.numeric(ideal_point)) %>% group_by(Date) %>% summarise(sum(ideal_point))

experiment_assign %>% filter(is.na(ideal_point)) %>% group_by(Date) %>% dplyr::summarise(n())

# experiment_assign %>% filter(Date == "2017-10-19", is.na(ideal_point)) 
```


```{r, warning=F}
set.seed(123456)

sample_30 <- sample(size = 30, unique((experiment_assign %>% filter(treat == "0"))$user_ids)) 

experiment_assign %>% filter(user_ids %in% sample_30) %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, color = user_ids, group = user_ids)) + geom_line() + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id") + labs(title = "A sample of 30 from Control") 

 # + theme(legend.position = "none")

experiment_assign %>% filter(treat == "0", Date %in% c("2017-10-13", "2017-10-16", "2017-11-27", "2018-02-01") ) %>%  
  ggplot(aes(x=ideal_point, color = Date)) + geom_density(alpha=0.5)


experiment_assign %>% filter(treat == "0", party_ID == "Republican", Date %in% c("2017-10-16", "2017-11-27") ) %>% 
  ggplot(aes(x=ideal_point, color = Date, fill = Date)) + geom_density(alpha=0.3) + labs(title = "Republican Control")

experiment_assign %>% filter(treat == "0", party_ID == "Democrat", Date %in% c("2017-10-16", "2017-11-27") ) %>% 
  ggplot(aes(x=ideal_point, color = Date, fill = Date)) + geom_density(alpha=0.3) + labs(title = "Democrat Control")

# table(experiment_assign$treat)
```

```{r}
experiment_assign %>% filter(treat == "1", party_ID == "Democrat", ideal_point > 0) %>% summarise(n_distinct(user_ids))
```



```{r}
# arrange a single day's following data
user_ids.txt <- list.files("All_Data/Friends/2017-10-13", pattern="[0-9].txt")

user_ids <- as.numeric(gsub("([0-9]+).*$", "\\1", user_ids.txt))

filenames <- list.files("All_Data/Friends/2017-10-13", pattern="[0-9].txt", full.names = T)

network_ids <- lapply(filenames, scan)

user_friends_list <- list()
for (i in seq_along(user_ids))
{
  user_friends_list[[i]] <- list(user_ids[i], 
                                 network_ids[[i]])
}

# user_friends_list[[345]]
```


```{r, message=F}
# user_friends_list[[1]][[1]]
# user_friends_list[[1]][[2]]
# estimateIdeology2(user_friends_list[[1]][[1]], user_friends_list[[1]][[2]])


ideal_point <- c()

for (i in seq_along(user_friends_list)) {
  
  skip_to_next = FALSE
  
  tryCatch(  ideal_point[i] <- estimateIdeology2(user_friends_list[[i]][[1]], user_friends_list[[i]][[2]]), 
             error = function(e) { skip_to_next = TRUE})
  
  if(skip_to_next) { next } 
}

ideal_point
```




# Current ideal points

```{r, warning=F}
# friends = results = ideal_point = vector("list")
# 
# id_str <- final_assignments$id_str
# 
# # seq_along(user_ids)
# 
# for (i in 1:20) 
# {
#   # friends[[i]] = get_following(id_str[i])
#    friends[[i]] = rtweet::get_friends(id_str[i], n = Inf, retryonratelimit = F)
# }
```

```{r}
# issue
rtweet::get_friends("271184449", n = Inf, retryonratelimit = F)

# check
get_user_v2(token = bearer_token, user_ids = id_str[5])$user_id
get_user_v2(token = bearer_token, user_ids = id_str[15])$following_count
```


```{r}
load("friends.RData")

current_ideal_point<- c()
status <- c()
ids <- c()
for (k in 1:1238) {
  
  if (is.null(friends[[k]]))
  {
    
    status[k] = "LOST"
    ids[k] <- NA
  }
  else{
    ids[k] <- friends[[k]][1, 1]
    if (is.na(friends[[k]]$to_id[1]))
    {
      status[k] = "PRIVATE"
    }
    else {
      status[k] = "NORMAL"
    }
  }

    skip_to_next = FALSE
    tryCatch(
      current_ideal_point[k] <-
        estimateIdeology2(friends[[k]][1,1], friends[[k]]$to_id),
      error = function(e) {skip_to_next = TRUE}
    )

    if (skip_to_next) {next}
}

current_pull <- as_tibble(cbind(user_ids = unlist(ids), 
                ideal_point = current_ideal_point, Date = "2022-11-13",
                status)) %>% mutate(ideal_point = ifelse(status == "NORMAL", ideal_point, NA)) 

current_pull <- rbind(current_pull, c(NA,NA,"2022-11-13","LOST"))
current_pull$user_ids <- final_assignments$id_str


current_ip <- current_pull

table(current_pull$status)

current_ip %>% filter(status == "NORMAL")

# save(current_ip, file = "current_ip.RData")
```


```{r}
full_experiment <- rbind(experiment, current_pull %>% select(-status))

full_experiment$ideal_point <- as.numeric(full_experiment$ideal_point)
```


```{r number of participants each day}
full_experiment_assign <- left_join(full_experiment, final_assignments, by=c("user_ids" = "id_str")) %>% 
  mutate(ideal_point = as.numeric(ideal_point))%>% tidyr::drop_na(ideal_point, treat)

full_experiment_assign %>% 
  mutate(ideal_point = ifelse(ideal_point == Inf, 5, ideal_point)) %>% 
  mutate(ideal_point = ifelse(ideal_point == -Inf, -5, ideal_point))

full_experiment_assign %>% group_by(Date) %>% summarise(n())

save(full_experiment_assign, file = "full_experiment_assign.RData") 
# this save all user info, assignment, ideal point on each day of experiment and 2022-11-13
```



```{r}
final_assignments$status <- current_pull$status


table(final_assignments$status)

table((final_assignments %>% filter(status == "LOST"))$party_ID)

table((final_assignments %>% filter(status == "PRIVATE"))$party_ID)
```




```{r, fig.width=8, fig.height=4}
full_experiment_assign %>% filter(Date %in%  c("2017-11-27","2022-11-13") ) %>% ggplot(aes(x=ideal_point, color = party_ID)) + geom_density(alpha=0.3) + facet_wrap(~Date)
```


# Current and Past

```{r, warning=F}
# new plots
full_experiment_assign %>% filter(treat == "1", Date %in% c( "2017-10-16", "2018-02-01", "2022-11-13") ) %>% 
  ggplot(aes(x=ideal_point, color = Date)) + geom_density(alpha=0.3) + labs(title = "Treatment")


full_experiment_assign %>% filter(treat == "1", Date %in% c("2017-10-13")) %>% 
  ggplot(aes(y=ideal_point, x = party_ID)) + geom_boxplot()+ labs(title = "Treatment 2017")


full_experiment_assign %>% filter(treat == "1", Date %in% c("2022-11-13")) %>% 
  ggplot(aes(y=ideal_point, x = party_ID)) + geom_boxplot()+ labs(title = "Treatment 2022")


# old plots
experiment_assign %>% filter(treat == "1", party_ID == "Republican", Date %in% c("2017-10-16", "2017-11-27", "2018-02-01")) %>%
  ggplot(aes(x=ideal_point, color = Date, fill = Date)) + geom_density(alpha=0.3) + labs(title = "Republican Treatment")

experiment_assign %>% filter(treat == "1", party_ID == "Democrat", Date %in% c("2017-10-16", "2017-11-27", "2018-02-01")) %>%
  ggplot(aes(x=ideal_point, color = Date, fill = Date)) + geom_density(alpha=0.3) + labs(title = "Democrat Treatment")

# new plots
full_experiment_assign %>% filter(treat == "1",party_ID == "Republican",Date %in% c("2017-11-27", "2022-11-13") ) %>%
  ggplot(aes(x=ideal_point)) + geom_density(alpha=0.3) + labs(title = "Republican Treatment") + facet_wrap(~Date)

full_experiment_assign %>% filter(treat == "1", party_ID == "Democrat", Date %in% c("2017-11-27", "2022-11-13") ) %>%
  ggplot(aes(x=ideal_point)) + geom_density(alpha=0.3) + labs(title = "Democrat Treatment") + facet_wrap(~Date)

full_experiment_assign %>% filter(treat == "1", Date %in% c("2017-11-27", "2022-11-13") ) %>%
  ggplot(aes(x=ideal_point, color = party_ID)) + geom_density(alpha=0.3) + labs(title = "All Treatment") + facet_wrap(~Date) + theme(legend.position = "none")


full_experiment_assign %>% filter(treat == "1", Date %in% c("2017-11-27", "2022-11-13") )  %>% group_by(Date) %>% summarise(n())

full_experiment_assign %>% filter(treat == "1", Date %in% c("2017-11-27", "2022-11-13") )  %>% group_by(Date, party_ID) %>% summarise(n())
```


```{r}
# new individual ts plots
set.seed(123456)

sample_50 <- sample(size = 50, unique((full_experiment_assign %>% filter(treat == "1"))$user_ids))

full_experiment_assign %>% filter(user_ids %in% sample_50) %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, color = user_ids, group = user_ids)) + geom_line() + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + labs(title = "A sample of 50 from Treatment") + theme(legend.position = "none")
```



```{r}
quantile(full_experiment_assign$ideal_point, c(0.01, 0.025))

full_experiment_assign <- full_experiment_assign %>% 
  mutate(ideal_point = ifelse(ideal_point == Inf, 5, ideal_point)) %>% 
  mutate(ideal_point = ifelse(ideal_point == -Inf, -5, ideal_point))

summary(full_experiment_assign$ideal_point)

# end the experiment and now 
full_experiment_assign %>% 
  filter( Date %in% c("2017-10-16", "2022-11-13"), party_ID == "Democrat") %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID, treat)  %>% 
  group_by(treat) %>% 
  summarise(mean(Difference, na.rm =T))

full_experiment_assign %>% 
  filter( Date %in% c("2017-10-16", "2022-11-13"), party_ID == "Republican") %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID, treat)  %>% 
  group_by(treat) %>% 
  summarise(mean(Difference, na.rm =T))


# during the experiment
full_experiment_assign %>% 
  filter( Date %in% c("2017-10-16", "2017-11-28"), party_ID == "Democrat") %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID, treat)  %>% 
  group_by(treat) %>% 
  summarise(mean(Difference, na.rm =T))

full_experiment_assign %>% 
  filter( Date %in% c("2017-10-16", "2017-11-28"), party_ID == "Republican") %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID, treat)  %>% 
  group_by(treat) %>% 
  summarise(mean(Difference, na.rm =T))
```



```{r}
full_experiment_assign %>% 
   filter( Date %in% c("2017-10-16"), party_ID == "Republican") %>% 
   select(user_ids)

correct_rep <- full_experiment_assign %>% 
   filter( Date %in% c("2017-10-16"), party_ID == "Republican") %>% 
  filter(ideal_point >= 0 ) %>% select(user_ids)

full_experiment_assign %>% 
  filter(user_ids %in% correct_rep$user_ids) %>% 
  filter( Date %in% c("2017-10-16", "2022-11-13"), party_ID == "Republican") %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID, treat)  %>% 
  group_by(treat) %>% 
  summarise(mean(Difference, na.rm =T))

# t.test
Rep_difference <- full_experiment_assign %>% 
  filter(user_ids %in% correct_rep$user_ids) %>% 
  filter( Date %in% c("2017-10-16", "2022-11-13"), party_ID == "Republican") %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID, treat) %>% 
  distinct(user_ids, .keep_all = T)


t.test((Rep_difference %>% filter(treat == 0))$Difference, 
      (Rep_difference %>% filter(treat == 1))$Difference)
```





```{r}
full_experiment_assign %>% 
   filter( Date %in% c("2017-10-16"), party_ID == "Democrat") %>% 
   select(user_ids)


correct_dem <- full_experiment_assign %>% 
   filter( Date %in% c("2017-10-16"), party_ID == "Democrat") %>% 
  filter(ideal_point <= 0 ) %>% select(user_ids)

full_experiment_assign %>% 
  filter(user_ids %in% correct_dem$user_ids) %>% 
  filter( Date %in% c("2017-10-16", "2022-11-13"), party_ID == "Democrat") %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID, treat)  %>% 
  group_by(treat) %>% 
  summarise(mean(Difference, na.rm =T))


Dem_difference <- full_experiment_assign %>% 
  filter(user_ids %in% correct_dem$user_ids) %>% 
  filter( Date %in% c("2017-10-16", "2022-11-13"), party_ID == "Democrat") %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID, treat)



t.test((Dem_difference %>% filter(treat == 1))$Difference, 
      (Dem_difference %>% filter(treat == 0))$Difference)

mean((Dem_difference %>% filter(treat == 0))$Difference)
mean((Dem_difference %>% filter(treat == 1))$Difference)
```




```{r}
# Treat
full_experiment_assign_withDiff <- full_experiment_assign %>% 
  filter(treat == "1", Date %in% c("2017-11-27", "2022-11-13")) %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID)

plot(full_experiment_assign_withDiff$Difference)

# full_experiment_assign_withDiff %>% filter(user_ids %in% "1017373046") %>% 
# ggplot(aes(x=as.Date(Date), y=ideal_point, color = user_ids, group = user_ids)) + geom_line() + 
#   labs(y = "Estiamted Ideal Point", x= "Date", color = "user id") + theme(legend.position = "none")


full_experiment_assign_withDiff %>% filter(abs(Difference) >= 1) %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, color = party_ID, group = user_ids)) + geom_line(size = 1) + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id") 

full_experiment_assign_withDiff %>% filter(abs(Difference) >= 1, party_ID == "Democrat") %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, group = user_ids)) + geom_line(size = 1)  + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + theme(legend.position = "none")

full_experiment_assign_withDiff %>% filter(abs(Difference) >= 1, party_ID == "Republican") %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, group = user_ids)) + geom_line(size = 1) + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + theme(legend.position = "none")
```
```{r, fig.width=7, fig.height=3}
full_experiment_assign_withDiff %>% filter(abs(Difference) >= 0.5) %>% 
  ggplot(aes(x=as.Date(Date), y=ideal_point, color = user_ids, group = user_ids)) + geom_line() + geom_hline(yintercept = 0, size = 2) + labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + theme(legend.position = "none") + facet_wrap(~party_ID)
```


```{r}
# Control
full_control_assign_withDiff <- full_experiment_assign %>% 
  filter(treat == "0", Date %in% c("2017-11-27", "2022-11-13")) %>% 
  group_by(user_ids) %>% 
  mutate(n = n()) %>% 
  filter(n == 2) %>% 
  mutate(Difference = diff(ideal_point)) %>% 
  select(user_ids, ideal_point, Date, Difference, party_ID)

plot(full_control_assign_withDiff$Difference)

full_control_assign_withDiff %>% filter(abs(Difference) >= 1) %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, color = party_ID, group = user_ids)) + geom_line(size = 1) + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  

full_control_assign_withDiff %>% filter(abs(Difference) >= 1, party_ID == "Democrat") %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, group = user_ids)) + geom_line(size = 1)  + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + theme(legend.position = "none")

full_control_assign_withDiff %>% filter(abs(Difference) >= 1, party_ID == "Republican") %>% 
ggplot(aes(x=as.Date(Date), y=ideal_point, group = user_ids)) + geom_line(size = 1) + 
  labs(y = "Estiamted Ideal Point", x= "Date", color = "user id")  + theme(legend.position = "none")
```


```{r}
friends_1017373046 <- rtweet::get_friends("1017373046", n = Inf, retryonratelimit = F)$to_id

sim <- c()
for (i in 1:5000)
{sim[i] <- estimateIdeology2(user = "1017373046", friends = friends_1017373046, verbose = F)}

sd(unlist(sim))
```


# case study

```{r}
# Weak Republican
full_experiment_assign %>% filter(user_ids == "81681105")
tweets_81681105 <- get_timeline(user = "81681105", n = Inf)

full_experiment_assign %>% filter(user_ids == "81681105") %>% ggplot(aes(x=as.Date(Date), y=ideal_point))  + geom_line() + 
  labs(y = "Estiamted Ideal Point", x= "Date") + theme(legend.position = "none")
```

  
```{r}
# Strong Republican
full_experiment_assign %>% filter(user_ids == "1537752216")
tweets_1537752216 <- get_timeline(user = "1537752216", n = Inf)

full_experiment_assign %>% filter(user_ids == "1537752216") %>% ggplot(aes(x=as.Date(Date), y=ideal_point))  + geom_line() + 
  labs(y = "Estiamted Ideal Point", x= "Date") + theme(legend.position = "none")
```

```{r}
# Strong Republican
full_experiment_assign %>% filter(user_ids == "918585656099586048")
tweets_918585656099586048 <- get_timeline(user = "918585656099586048", n = Inf)

full_experiment_assign %>% filter(user_ids == "918585656099586048") %>% ggplot(aes(x=as.Date(Date), y=ideal_point))  + geom_line() + labs(y = "Estiamted Ideal Point", x= "Date") + theme(legend.position = "none")
```


```{r}
# Weak Democrat
full_experiment_assign %>% filter(user_ids == "419650051")
tweets_419650051 <- get_timeline(user = "419650051", n = Inf)

full_experiment_assign %>% filter(user_ids == "419650051") %>% ggplot(aes(x=as.Date(Date), y=ideal_point))  + geom_line() + 
  labs(y = "Estiamted Ideal Point", x= "Date") + theme(legend.position = "none")
```

```{r}
# Strong Democrat
full_experiment_assign %>% filter(user_ids == "403290010")
tweets_403290010 <- get_timeline(user = "403290010", n = Inf)

full_experiment_assign %>% filter(user_ids == "403290010") %>% ggplot(aes(x=as.Date(Date), y=ideal_point))  + geom_line() + 
  labs(y = "Estiamted Ideal Point", x= "Date") + theme(legend.position = "none")
```



```{r}
load("All_Data/Respondent Twitter Timelines/Respondent Twitter Timelines.Rdata")

min(respondent_tweets$created)
max(respondent_tweets$created)

respondent_tweets %>% group_by(id_str) %>% dplyr::summarise(n())

respondent_tweets %>% filter(id_str == "403290010")
```


# Two bots 

```{r}
load("All_Data/Tweets by Conservative Bot.Rdata")
load("All_Data/Tweets by Liberal Bot.Rdata")

# Conservative 942200215020408832
# Liberal 941807349504847878

n_distinct(as.Date(conservative_bot_tweets$created))
n_distinct(as.Date(liberal_bot_tweets$created))

hist(as.Date(conservative_bot_tweets$created), breaks = 117)
hist(as.Date(liberal_bot_tweets$created), breaks = 112)
```


# Other thoughts

```{r}
f_counts <- c()
for (i in 1:10) 
{
f_counts[i] <- (get_user_v2(token = bearer_token, user_ids = id_str[i]))$following_count
}
f_counts
```


```{r}
for (i in 1:10) 
{
  results[[i]] = estimateIdeology2(user = user_ids[[i]],  
                                  friends = friends[[i]], verbose = F)
  
  ideal_point[[i]] = mean(c(results[[i]]$samples[,1,2],results[[i]]$samples[,2,2]))
}
```


# New (more) opinion leaders

```{r}
load("refdataCA.rdata")
length(refdataCA$colnames)

tweetscores::refdataCA$colmass
tweetscores::refdataCA$colnames
tweetscores::refdataCA$id
tweetscores::refdataCA$qs

tweetscores::refdataCA$colcoord
```

```{r}
load("posterior_samples.rdata")
dim(posterior_samples$alpha)
length(posterior_samples$gamma)


View(posterior_samples$alpha)


```


```{r}
load("Final Op Leader Twitter Data.Rdata")
final_op_data[,c(3,1)]$screen_name

op <- read.csv("op_leader_edges_juncheng.csv")


names(final_op_data)

table(final_op_data$lang)
table(final_op_data$location)
n_distinct(final_op_data$screen_name)
```



# Try academictwitteR

```{r}
library(academictwitteR)
set_bearer()
```


```{r}
tweets <-
  get_all_tweets(
    query = "#BlackLivesMatter",
    start_tweets = "2020-01-01T00:00:00Z",
    end_tweets = "2020-01-05T00:00:00Z",
    file = "blmtweets",
    data_path = "data/",
    n = 10,
  )

tweets <-
  get_all_tweets(
    users = c("jack", "cbarrie"),
    start_tweets = "2020-01-01T00:00:00Z",
    end_tweets = "2020-01-05T00:00:00Z",
    file = "blmtweets",
    n = 1000
  )
```





# data pulling work

#  pull friends timeline
```{r}
load("friends.RData")

for (i in seq_along(id_str)) {
dir.create(path = paste("timeline_friends/", id_str[i], sep = ""), showWarnings = FALSE)
}


for (i in seq_along(id_str)) {
  
  respondent <- friends[[i]]$from_id[1]
  respondent_friends <- friends[[1]]$to_id

  for (j in seq_along(respondent_friends)) 
  {
    skip_to_next = FALSE
    
    id <- respondent_friends[j]
    
      tryCatch(
        write.csv(apply(get_timeline(id, n = Inf, retryonratelimit = T), 2, as.character),  
                  paste("timeline_friends/", respondent, "/timeline_", id, ".csv", sep = ""), row.names = F), 
        error = function(e) {skip_to_next = TRUE}
      )
      
      if (skip_to_next) {next}
  }
  
}
```





consistency 

political elites 

DW-nominate score 

look at the regular people 











